---
title: "Week 2 SMU 6306"
author: "Jonathan Franks"
date: "January 21, 2018"
output: html_document

---

## Question 1

####What is a basic workflow for reproducible research?

A basic workflow for reproducible research contains three componetes, data gathering, data anaylsis, results presentaton. 


####What are five practical tips for making research reproducible?

1. Document everything!
2. Everything is a (text) file.
3. All files should be human readable.
4. Explicitly tie your files together
5. Have a plan to organize, store, and make your files available


####Give an example of how you might implement each tip.

1. Create a notebook detailing the research and refiniment of the process.
2. Use universal formats like .txt for the storage of the created notebook.
3. Use comments and straight forward coding pratices.
4. Use relative path names to tie documents together in the project folder.
5. Use github or other file storage software suites.


####Which one of these do you think will be the most difficult?
1. Notebook creation and straight forward documentation. 


## Question 2

Inital Code to load data
```{r, echo=TRUE}
# We will be using the built-in dataset airquality which has daily air quality 
##measurements in New York from May to September 1973
str(airquality)
```
####Part a

```{r, echo=TRUE}
plot(x=airquality$Month, y=airquality$Temp, xlab="Month", ylab="Temperature", main="Temperature by Month")
```


####Part b

```{r, echo=TRUE}
plot(x=airquality$Temp, y=airquality$Ozone, xlab="Temperature", ylab="Ozone", main="Temperature vs Ozone")
```

## Question 3

####Part a

```{r, echo=TRUE}
plot(x=pressure$pressure, y=pressure$temperature, xlab="Pressure", ylab="Temperature", main="Temperature vs Pressure" )
```
####Part b

```{r, echo=TRUE}
plot(y=pressure$pressure, x=pressure$temperature, ylab="Pressure", xlab="Temperature", main="Pressure vs Temperature" )
```



